Web Page Visualization Code

### 2024-08-25 Webpage Visualizations Code.Rmd
changed files

plt.figure(figsize=(10, 6))
all_threads.groupby(all_threads['Date'].dt.to_period('M')).size().plot(kind='line')
plt.title('Number of Threads Over Time')
plt.xlabel('Month')
plt.ylabel('Number of Threads')
plt.tight_layout()
plt.savefig('images and tables/number_of_threads_over_time.png')
plt.show()
```

>>>>

plt.figure(figsize=(10, 6))
all_threads.groupby(all_threads['Date'].dt.to_period('M')).size().plot(kind='line')
plt.title('Number of Threads Across All Newsgroups Over Time')
plt.xlabel('Month')
plt.ylabel('Number of Threads')
plt.tight_layout()
plt.savefig('images and tables/number_of_threads_over_time.png')
plt.show()
```
